Dirac neutrino mass generation from Majorana messenger

### 2019-08-06 draft.tex
lc

The rest of the paper is organized as follows. In the next section we present the model and the particle content. In the section~\ref{sec:ScaMassSpect} we study the scalar mass spectrum after spontaneous symmetry breaking. In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses. In section~\ref{sec:LFV} we show the lepton flavor violation (LFV)experimental  constraints. Finally, in the section~\ref{sec:DM} we present the viable DM candidates.

@@

% \subsection{Scalar mass spectrum}
%\label{sec:ScaMassSpect}
To establish the scalar spectrum we expand the scalar fields as
%
\begin{align*}
  H = \begin{pmatrix}G^{\pm} \\ \frac{1}{\sqrt{2}} (\varphi+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
  \eta = \begin{pmatrix}\eta^{+} \\ \frac{1}{\sqrt{2}}(\eta_R+i\eta_I) \end{pmatrix} \,,\\
  S = \frac{1}{\sqrt{2}} (S_R+v_{S}+iS_I)\,,&\hspace{1cm}\sigma = \frac{1}{\sqrt{2}} (\sigma_R+i\sigma_I),
\end{align*}
%
with $v= 246.22$ GeV.  
By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
%
\begin{align*}
    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  v^2 + \lambda_{1}  v_S\right)\,,  &
    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  v^{2}_{S} + \lambda_{1}  v^2\right)\,.
\end{align*}
%
Of the original twelve scalar degrees of freedom in the model\todo{what are the twelve?}, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorbed four of these (Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$). There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar state ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar state ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar pairs ($\eta^{\pm}$). The mass spectrum for the scalar sector is given by
\begin{align*}
    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{3} \upsilon^{2}_{H} + \lambda_{5} \upsilon^{2}_{s} )\,, \\
    m_{H}^{2} &= \lambda_{H} \upsilon_{H}^{2} + \mathcal{O}()\,, \\
    m_{S}^{2} &= \lambda_{S} \upsilon_{S}^{2} + \mathcal{O}()\,.
\end{align*}
%
The neutral mass eigenstate are defined as
%
\begin{align*}
    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
\end{align*}
%
where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\mu \upsilon_{H} \upsilon_{S}$\,. The corresponding mass eigenvalues are
\begin{align*}
    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c^{2}} \right)\,, \\
     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c^{2}} \right)\,,
\end{align*}

\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generated at one loop-level according to the diagram in  fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\mu \upsilon_{H} \upsilon_{S}}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is the loop function, $M_{\psi_{a}}$ is the fermion mass  and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the two CP-even (CP-odd) mass eigenstates. To obtain neutrino masses it is necessary that $\mu \neq 0$. In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large. Another possibility is small values of $\mu$, this suppress the value of the neutrino masses. The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one fermion $\psi_R$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}. In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).

>>>>

The rest of the paper is organized as follows. In the next section we present the model and the particle content. In the section~\ref{sec:ScaMassSpect} we study the scalar mass spectrum after spontaneous symmetry breaking. In section~\ref{sec:Neutrinos} We present a mechanism to generate Dirac neutrino masses. In section~\ref{sec:LFV} we show the lepton flavor violation (LFV) experimental  constraints. Finally, in the section~\ref{sec:DM} we present the viable DM candidates.

@@

% \subsection{Scalar mass spectrum}
%\label{sec:ScaMassSpect}
To establish the scalar spectrum we expand the scalar fields as
%
\begin{align*}
  H = \begin{pmatrix}G^+ \\ \frac{1}{\sqrt{2}} (\varphi+v_H+iG) \end{pmatrix} \,,&\hspace{1cm}
  \eta = \begin{pmatrix}\eta^{+} \\ \frac{1}{\sqrt{2}}(\eta_R+i\eta_I) \end{pmatrix} \,,\\
  S = \frac{1}{\sqrt{2}} (S_R+v_{S}+iS_I)\,,&\hspace{1cm}\sigma = \frac{1}{\sqrt{2}} (\sigma_R+i\sigma_I),
\end{align*}
%
with $v= 246.22$ GeV.  
By minimizing the scalar potential we find that the mass-squared parameters $\mu_H^2$ and $\mu_S^2$
%
\begin{align*}
    \mu^{2}_{H} =& -\frac{1}{2}\left( \lambda_{H}  v^2 + \lambda_{1}  v_S\right)\,,  &
    \mu^{2}_{S} =& -\frac{1}{2}\left( \lambda_{S}  v^{2}_{S} + \lambda_{1}  v^2\right)\,.
\end{align*}
%
Of the original twelve scalar degrees of freedom in the model, $W^{\pm}$, $Z^{0}$ and $Z^{\prime}$ absorve four of them (the Goldstone bosons $G^{\pm}$,$G$ and $S_{I}$). There is a physical neutral CP-even Higgs state ($\varphi$), one scalar state ($S_{R}$), two CP-even scalar states ($\sigma_{R}$ and $\eta_{R}$), two CP-odd scalar states ($\sigma_{I}$ and $\eta_{I}$) and one charged scalar ($\eta^{\pm}$). The mass spectrum for the scalar sector is given by
\begin{align*}
    m_{\eta^{\pm}}^{2} &= \mu_{\eta}^{2} + \frac{1}{2} (\lambda_{3} \upsilon^{2}_{H} + \lambda_{5} \upsilon^{2}_{s} )\,, \\
    m_{H}^{2} &= \lambda_{H} \upsilon_{H}^{2} + \mathcal{O}()\,, \\
    m_{S}^{2} &= \lambda_{S} \upsilon_{S}^{2} + \mathcal{O}()\,.
\end{align*}
%
The neutral mass eigenstate are defined as
%
\begin{align*}
    \begin{pmatrix}\chi_{(R,I)_{1}} \\ \chi_{(R,I)_{2}} \end{pmatrix} =& \begin{pmatrix} c_{\theta_{(R,I)}} & -s_{\theta_{(R,I)}} \\ s_{\theta_{(R,I)}} & c_{\theta_{(R,I)}} \end{pmatrix} \begin{pmatrix}\sigma_{(R,I)} \\ \eta_{(R,I)} \end{pmatrix} \,,
\end{align*}
%
where $\tan2\theta_{(R,I)} = \pm2c/(b-a)$ and we defined $a = m^{2}_{\eta^{\pm}} + \frac{1}{2}\lambda_{7} \upsilon^{2}_{H}$, $b = \mu^{2}_{\sigma}+\frac{1}{2}(\lambda_{2} \upsilon^{2}_{H} + \lambda_{4} \upsilon^{2}_{S})$ and $c = \frac{1}{2}\mu \upsilon_{H} \upsilon_{S}$\,. The corresponding mass eigenvalues are
\begin{align*}
    m_{\chi_{R(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} + 4c^{2}} \right)\,, \\
     m_{\chi_{I(1,2)}}^{2} &= \frac{1}{2} \left(a + b \mp \sqrt{(a-b)^{2} - 4c^{2}} \right)\,,
\end{align*}

On the other hand, we assume that the heavy Majorana fermions are already in the diagonal basis defined as $
\begin{pmatrix}
  \psi_1 &
  \psi_2 &
  \psi_3
\end{pmatrix}^{\operatorname{T}}
$, with masses $M_{\psi_a}$ ($a=1,2,3$).
\section{Neutrinos}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop generation of Dirac neutrino mass}
\label{fig:zee}
\end{figure}
%
 The Dirac neutrino mass matrix in this model is generated at one loop-level according to the diagram in  fig.~\ref{fig:zee}. The expression for $\mathcal{M}_{\nu}$ is given by~\cite{Reig:2018mdk}
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{\mu \upsilon_{H} \upsilon_{S}}{32 \pi^{2}} \sum_{a=1}^{3} \frac{h_{i a} M_{\psi_{a}}y^{\dagger}_{a j}} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}} \left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{a}}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{a}}} \right) \right] + (R \to I)\,,
\end{align}
%
where $F(m_{S_{\beta}}^{2}/M_{\psi}^{2}) = m_{S_{\beta}}^{2}\log(m_{S_{\beta}}^{2}/M_{\psi})/(m_{S_{\beta}}^{2}-M_{\psi})$ is the loop function, $M_{\psi_{a}}$ is the fermion mass  and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the two CP-even (CP-odd) mass eigenstates. To obtain neutrino masses it is necessary that $\mu \neq 0$. In addition, To explain the suppression of the mass matrix, it is usually assumed that the mass of the mediator fermions is very large. Another possibility is small values of $\mu$, this suppress the value of the neutrino masses. The structure of the effective neutrino mass matrix is given by the product $(M_{\nu})_{ij} \propto h_{i a} y_{a j}$, which is similar to the structure of the neutrino mass matrix for the tree-level seesaw mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. If only one fermion $\psi_R$ is added, we will have two massless neutrinos, which does not agree with the current data obtained from the neutrino experiments~\cite{deSalas:2017kay}. In our case, we will assume the existence of three fermions, generating Dirac scotogenic masses for the two neutrinos ($\nu_{k}$ is massless due to the assignment of charges).
